\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.55in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-4pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\small % or \footnotesize to compress further

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Kodidela Sanjay Reddy} \\ \vspace{1pt}
    \small \href{mailto:sanjay.kodidela@gmail.com}{\faEnvelope\ sanjay.kodidela@gmail.com} $|$
    \small \faPhone\ +91-9154443106 $|$
    \small \href{https://www.linkedin.com/in/sanjay-reddy-kodidela-824323209/}{\faLinkedin\ LinkedIn} $|$
    \small \href{https://github.com/SanjayReddy91}{\faGithub\ GitHub}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {B.Tech., Computer Science and Eng.}{2020 -- 2024}
        {NIT Rourkela}{CGPA: 8.29/10.0}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Member of Technical Staff}{Jul 2024 -- Present}
        {Oracle Corporation}{}
        \resumeItemListStart
            \resumeItem{Developed scalable REST APIs and microservices for Fleet Application Management System (FAMS) service in OCI using Java and Dropwizard framework.}
            \resumeItem{Contributed to scalable backend services ensuring seamless integration and deployment within Oracle Cloud Infrastructure.}
        \resumeItemListEnd

    \resumeSubheading
        {Software Engineer Intern}{May 2023 -- Jul 2023}
        {Oracle Corporation}{}
        \resumeItemListStart
            \resumeItem{Built a lightweight agent in GoLang using gRPC and go-oci-sdk to automate client command execution on selected VMs in OCI.}
            \resumeItem{Enabled efficient orchestration of remote VM tasks by designing and integrating a custom client-agent communication pipeline.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Hybrid Battery for UAVs} $|$ \emph{C, Python}}{}
    \resumeItemListStart
      \resumeItem{Designed a hybrid battery-supercapacitor model to handle variable UAV workloads.}
      \resumeItem{Implemented flight and energy simulation using C; analyzed parameters using Python libraries.}
      \resumeItem{Enabled optimized power management for UAVs by determining ideal energy switching points.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Fleet Agent} $|$ \emph{gRPC, GoLang, go-oci-sdk}}{}
    \resumeItemListStart
      \resumeItem{Built an automation agent to manage and encrypt commands for OCI VM instances.}
      \resumeItem{Used GoLang, gRPC, and go-oci-sdk to automate command execution and artifact deployment.}
      \resumeItem{Improved cloud operational efficiency by securely managing VM lifecycle tasks.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL PROFILES-----------
\section{Technical Profiles}
\begin{flushleft}
    \small
    \textbf{\texttt{</>}} \href{https://github.com/SanjayReddy91}{GitHub} \quad
    \textbf{\texttt{</>}} \href{https://www.linkedin.com/in/sanjay-reddy-kodidela-824323209/}{LinkedIn}
\end{flushleft}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
        \textbf{Languages}{: Java, Rust, C, C++, Go, JavaScript, HTML} \\
        \textbf{Technologies}{: Dropwizard, gRPC} \\
        \textbf{Databases}{: Oracle DBMS} \\
        \textbf{Courses}{: Data Structures, OS, Networks, ML, Cloud Computing} \\
        \textbf{OS}{: Windows, Linux}
    }}
\end{itemize}

%-----------ACHIEVEMENTS---------------
\section{Achievements}
\resumeSubHeadingListStart
    \resumeItemListStart
        \resumeItem{OCI Architect Associate Certification, 2025.}
        \resumeItem{OCI Generative AI Professional Certification, 2025.}
        \resumeItem{OCI Foundations Associate Certification, 2025.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
